\documentclass[a4paper,12pt]{book}
\usepackage{ae}
\usepackage{aeguill}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[left=1cm, right= 1cm, top=2cm, bottom = 2cm]{geometry}
\usepackage{array,multirow}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{amsfonts}
\usepackage{stmaryrd}
\usepackage{tcolorbox}
\usepackage{lmodern}



\newcommand{\Def}[2]{\begin{tcolorbox}[sharp corners, colback=white,colframe=red!90!black!75, title=Définition : #1]#2\end{tcolorbox}}
\newcommand{\Thr}[2]{\begin{tcolorbox}[sharp corners, colback=white,colframe=red!90!black!75, title=Théorème : #1]#2\end{tcolorbox}}
\newcommand{\Prop}[2]{\begin{tcolorbox}[sharp corners, colback=white,colframe=red!90!black!75, title=Proposition : #1]#2\end{tcolorbox}}
\newcommand{\Pre}[1]{\begin{tcolorbox}[sharp corners, colback=white,colframe=green!60!green!30!black!75, title=Preuve]#1\end{tcolorbox}}

\newcommand{\Meth}[2]{\begin{tcolorbox}[colback=white,colframe=green!60!green!30!black!75, title=Méthode :  #1]#2\end{tcolorbox}}
\newtheorem{Exe}{Exemple}[section]
\newtheorem{Exes}{Exemples}[section]
\newtheorem{Rem}{Remarque}[section]
\newtheorem{Rems}{Remarques}[section]

\def\R{\mathbb{R}}
\def\D{\mathbb{D}}
\def\C{\mathbb{C}}
\def\Q{\mathbb{Q}}
\def\N{\mathbb{N}}
\def\Z{\mathbb{Z}}
\def\K{\mathbb{K}}

\renewcommand{\thechapter}{\Roman{chapter}}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Roman{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\Roman{section}.\arabic{subsection}.\Alph{subsubsection}}
\title{Up yours, woke moralists. \\ We'll see who cancels who...}
\author{Mister Markert}

\begin{document}
\maketitle
\tableofcontents
teacher.markert\texttt{@}gmail.com
\par We need to subscribe to The Nation.
\par Also Scientific American, Real Engineering/Interesting Engineering, 2 minutes papers

\chapter{Mister Markert goes to the nuclear powerplant}
\section{Nuclear power : a booming industry}
\begin{itemize}
\item Over the last few years, nuclear energy has gone from the big bad wolf of energies to a possible green option.
\item When the American presidency was stolen from Donald Jonald Trump to Joe Robinette "Dark Brandon" Biden, the latter decided to go back on his predecessor's politics by taking undeniably green measures.
\item Yes, indeed, the United States are the biggest nuclear power and their numerous powerplants, which produce one half of their electricity, are as much a source of political tensions as an essential strategic asset.
\item Although the French own fewer powerplants (65 in France against 95 in the USA), they produce 75 percents of french energy and greatly contribute to their energetical sovreignty. But are we really that much safer than many others ?
\item When we are olf, perhaps our children will ask us : "What have you done to solve the nuclear waste issue ? And what about the risks of a nuclear meltdown ?" Let us hope we won't have to say to ourselves we could or should have acted sooner.
\item When the passage of time starts gnawing at our limbs, our seed may look upon us and ask "What did you do to resolve the nuclear waste problem ? And what about the nuclear accident risks ?" Let us hope that we won't have to say to ourselves we may have acted, or have needed to act earlier...
\item Andrew Tate is the biggest American nuclear waste dump.
\end{itemize}
Finland is a nuclear wasteland.

\subsection{Audioclip}
Answers :
\begin{itemize}
\item In the US, boost in production.
\item Fear and suspicion about the safety because of accidents. Also it costs a lot compared to everything (maintaining, building).
\item Plants were growing old and shut down.
\item Seems like half of powerplants would be shut down.
\item Plants can run whatever the meteo is. And it does not emits greenhouse gas.
\item Limit ability of association to limit greenhouse gas emitions.
\item Biden has put 6bn dollars in existing reactors.
\item New reactors mass-produced in the coming years.
\end{itemize}

\subsection{Very bad summary}
Let's go to Godzilland, there's a Gojira concert !
\par The January 2022 NPR article addresses nuclear power in the US, and addresses wheter or not it is viewed as a green source of energy, i.e. as part of the solution to the climate change issue.
\par The journalist mentions an AP survey that was conducted across all states, whose results are as follow.
\par The majority of US states want to develop nuclear power and use it to supplement renewable energy.
\par $\dfrac{1}{3}$ of the states don't want to, but it is because they already have efficient enough technology, or fruitful economic partnerships.
\par From this it appears that nuclear power is seen as a default temporary solution, used for lack of a better alternative.
\par (He illustrates this with the TVA, a federal power supplier whose aim is net zero power production [carbon neutrality], which hazs developed solar production, but which also operates three nucelar plants, and is planning to build once more.)
\par The journalist's conclusion is that it is a matter of risk assessment, and that it is part of president Joe (no -seph) Robinette "Darkest Brandon" Biden's political strategy. Not all countries think the same however, as shown by the European debate on using this energy source.

\subsection{Cartoon}
Fidel Castro holds the same image about nuclear power ; in the old days, he used to say that this was a power too dangerous to be placed in the hands of men, and he now says that it isn't that bad actually, considering how green it is. There is a contrast between the tree and the mushroom cloud, that had the same shape.
\par It seems climate change is that much of a desperate cause, we may need to go all nuclear. Plus, representing it as green is disturbing, seeing as even though there are no greenhouse gases produced, there is still the issue of nuclear waste.
\par The cartoon addresses how people have changed their mindes on nuclear energy. They thought of it as a danger because of nuclear weapons, nuclear incidents and nuclear waste. That perception has changed however. Nowadays, as climate change has become a topical issue and our main concern, nuclear power is viewed as a possible solution. It is considered an eco-friednly source because it releases very few carbon emissions, and is not as much polluting as fossil fuels.
\par Other cartoon : someone representing the ecological ideology is drawn like the cartoonist really had a grudge against someone. He is standing in a forest, deploring the lack of low emissions energy, while right next to a nuclear powerplant. It means that the ecological persons don't see the solutions that are right next to them. Climate change is still trezted as a problem, but the environmentalist doesn't see the clear solution. The cartoon says that nuclear power is a green solution.

\subsection{Very bad translation}
What is the status of the French nuclear strategy ? The country is at a crossroads.
\par France produces around 70 percents of its electricity thanks to its nuclear powerplants, whose lifespan has been increased to 50 years. The goal is to fuck that figure to 50 percent in 2035 in order to allow the development of renewable energies. A first symbolic step was done last year, when the to reactors of the Fessenheim powerplant were shut down. But while the fleet - made mainly in the 1980s - is starting to grow old, the country hasn't made a clear decision on it. In the end of 2020, there were 412 reactors in use in 33 countries.
\par France is the construction of 6 new generation WPR reactors, but the decision won't be taken before the next mandate, when the government is either changed or accepted back. Executive wants to wait for the Flamanville EPR unveiling, around the end of 2022, after many problems : it will have been late for 10 years, and its cost will have been multiplied by 3.    

\subsection{Very bad summary}
To compare the Rolls-Royce project and the EDF project : The EDF project costs more, the EDF project will produce electricity that will be more expensive for the consumers, the Rolls-Royce project is a cheap modular copy that wasn't taylor-made for the location (built off-site !), which allows it to skip costs, the EDF project was an alliance between countries, the Rolls-Royce one is an alliance between rich men from different nations and the Bri'ish. Rolls-Royce are a british company, a known sin. The Rolls-Royce reactor won't supply as much as an EDF one.
\par The EDF one costs around 53 billion pounds over 35 years, the Rolls-Royce will cost 22 billions. The SMR are smaller, and allows for economic competition. The consumers will have to pay more with the EDF one.
\par EDF is doing a bad state-owned thing because they're evil and communists. Rolls-Royce, however, is our guide through the dark ages of communism and will lead us to the real power of the freeest market.
\par The UK is in dire need of a green source of energy. Nuclear seemed like an option ten years ago, but after deciding some powerplants needed to be constructied, the government only started building one. It was with the French EDF, a public sector company. But there have been many problems with it, and the private Rolls-Royce company may be a solution.
\par Indeed, Rolls-Royce is putting a new type of reactors on the table. They seem to be everything that EDF won't do : they're cheaper, they don't have to be built in one spot and they won't push a deal as bad as the one EDF negociated. This is a prime example of the private sector entering an industry that was thought to be only taylored to gigantic public companies.
\par However, there may be a problem, with the output of the reactors, far lower than the EDF reactor's. And while Rolls-Royce believes in a world where many companies can produce their own SMR parts for these new modular reactors, the market is not made for it yet.
\par Real summary : The UK is assessing different options as regards to nuclear energy. They are currently involved with the French company EDF, but its British competitor Rolls-Royce is designing a new project. RR's project is three (3) times quicker to build and ten (10) times cheaper. Its energy output is, however, eight (8) times lower. Moreover, the RR project of modular technology would allow smaller companies to be involved, thus creating economic competition, something that would theoretically drive prices down.
\par That would in turn be a positive outcome for both the UK government and the consumers. New companies could then invest in this ecologic issue. Nuclear is a far more reliable option than other green energies. However, most of the UK's powerplants are old and decrepit.

\subsection{New audioclip}
\begin{itemize}
\item No ???? Energy energy energy (solar wind, hydro)
\item Second largest
\item Common misconception that it has something to do with nuclear war.
\item Nuclear power creates high temperature steam to spin turbines, and the fusion reaction is really contained. Nuclear weapons release a large amount of energy in one massive explosion
\item Zero-emission clean source, 466 million metric tons of carbon not produced thanks to nuclear powerplants in the USA in 2019, equivalent to removing a hundred million cars' worth of carbon from the roads.
\item Much higher : 1000 mW for a square mile of land for nuclear, 360 times more for wind (430 turbines) and around 75 times more space for solar (3 million).
\item Tiny amounts of fuel needed, and doesn't produce a lot of waste : very waste-efficient.
\item The total amount would fit in a football field at a depth of less than ten yards.
\item It can be recycled with thorium/salt reactors, or to create diamond batteries (Bristol university).
\item Highly hazardous, needs safe facilities for very long periods of time
\item When it goes wrong, it only goes nuclear explosion wrong. But the WNA remarks that it only happened three times in the history of humanity (17 000 cumulative reactor years, 33 countries).
\end{itemize}
The video was produced and edited by the nuclear energy institute.



\chapter{Mister Markert, new king of England ?}
Mind map : what is associated with the British Monarchy :\begin{itemize}
\item Queen Elizabeth was iconic, her replacement (Charles the Turd) isn't that much. Plus she reigned for 70 years, so she's the second-longest monarch in history.
\item The monarch is the head of state and of the anglican church.
\item Head of state : they rule, but do not reign. They don't have real political power, merely symbolic power. It is a national tradition, linking englishmen to their identities
\item Head of anglican church : Because of divorce guy, they have their own christianity variant
\item The current monarchs come from a german dynasty.
\item The royal family : lots of drama between the members of it (Meghan Markle and Megxit, who accused of racism other members of the royal family) and Prince Andrew.
\item No involvement in politics for the royal family : they are supposed to remain neutral.
\item Commonwealth : the british monarch is the head of the Commonwealth. The Commonwealth is a trade association between around 50 countries, 14 of which are monarchies. Most of them were part of the British Empire. There are exceptions : some countries like Cameroun and Rwanda came to the Commonwealth while they were not colonised by England.
\item The UK is not a secular state : the church is not separated from the state.
\end{itemize}
\section{Document number one : why does Britain still have a royal family ?}
Document from Sky News in 2020 (date is to be noted)
\begin{itemize}
\item They had a monarchy for centuries until 1649 and the civil war (Charles the First was executed because he opposed the parliament)
\item They don't have pover to passe laws, they have to sign all bills into law and open parliament. They have a symbolic role, hosting other heads of state and visiting other countries.
\item They have to support the monarch, be a model of family. This is not always the case... See Andrew and Epstein. They are involved in charities.
\item Morale boosters, represent link to history and tradition. They are still popular, 72 percent approval for queen (fictional depictions are very popular). They bring 1.8 bn pound to the UK government, almost half coming from tourism. The Queen creates business opportunities.
\item In 2019, they cost 67 million pounds.
\item It seems unlikely they'll be abolished, seeing their popularity. Even if there were disasters, like the Epstein interview or the Philip's car crash.
\item While she is popular, her successor Charles is less popular than most people in the family (seventh most popular), so this might change some opinions.
\end{itemize}




\chapter{The Markert-God of Man saves America's midterms}
\section{Trad} Midterms : the dangers of the political polarisation of voters \par
Even though there might still be surprising on election day, it is highly probable that on november 8th, Republicans will win back the majority of the House (or even of the Senate). It would fit in a remarkable continuity. Indeed, two years after the presidential election, in every midterms or neraly, the president's party loses grounds in Congress and generally in the Senate too.
\par This almost systemic back-and-forth of american politics raises an obvious question : don't political subjects have importance ? May we be forgiven for thinking that they do. In this endless trench war of the two grand parties, commentators never cease debating of the best communication strategies to talk well about any subject, endlessly one-upping each other in trying to find how to talk about a subject and what subjects to talk about. If no winning formula has been found, it's because there is none. 

\section{Cartoon}
Cartoon from befrome the midterms : we can see two anthopomorphised animals wearing stars and stripes ("old glory"), one elephant (standing for the republicans) lighting a big red midterms rocket and one donkey (democrats) with a very small rocket. The cartoon predicted that the 2022 midterms wowuld be a huge republican success.
\par But the cartoon's predictio was actually wrong, the midterms were not a big success for republicans. They didn't win the Senate (even though we don't have all the results, because of massive democrat fraud of course) as democrats had half (50 senators), which means a majority because the vp can cast a vote too. The only state we don't know about is Georgia (we won't know until the 6th of december). However, the GOP won seats in the House of Representatives. Among the 445 seats, they have 215 seats on the 218 needed for the majority in the house.
\par Four years ago, there were many cartoons about a red midterms wave. For the last midterms, there was merely a red ripple. In the New Yorker, they chose to portray the republican elephant as a surfer on a puddle, seemingly expecting a big wave.  
\par Recap : In the US, there are elections every two years, which are called "midterm elections" or "midtermes". \par If you are an Amercian voter, you actually vote for a lot of offices on three levels. \par On the federal level, you renew the House of Representatives, and one third of the Senate (they are located in Washington D.C. ; not all voters vote for a senator at the same time). \par On the state level, you may vote for the governor, as well as state representatives and state senators (as in almost all states there is a state Congress), and also for some judicial offices (different courts, the state Supreme Court) and elective offices. \par On a local level, in your county or your community, you can vote for various offices, ranging from sheriff to the headmaster of your school or your local judge. \par Finally, elections are organised by the states, which explains why on election day rules can vary from state to state.
\par For these specific midtermes : For these November 2022 midtermes, even though the final results are stille not in, what is sure is that the Trump-led Republican party had been expected to win or have a landslide victory (a "red wave"). In real life, however, if they do win it will be by a small margin, as they have just lost the Senate and are probably going to have a very small majority in the House. \par This will either create a gridlock situation or leave room for bipartisan bargaining ("reaching across the aisle"). \par This also casts doubt on Trump's ability to actually lead the GOP. The red wave has failed to materialise, and Trump is not surfing his way back into the White House any time soon.


















\chapter{Press Review}
\section{Semaine du 12 au 16 septembre 2022}
\subsection{UK}
Who is Queen Elizabeth ? Someone dead. But who was she before ? First, the Queen was a great electro musician. Second, she has been queen for 70 years, and saw a lots of changes, like sending the first royal email. She was also very popular (around 79 percents of approval). She was crowned at the age of 27. Britain became a country for old men. And women. Most women are now in the labour force. There has been much social progress during her reign. From Alan Turing that was chemically castrated and killed himself to a world more accepting.
\par But most of all, this is under her reign that monarchy lost more and more popularity. The queen said almost nothing of importance when she talked, which gave her the reputation of an enigma. She attended a lot of public ceremonies despite her old age, gave herself the reputation of a hard-working woman. Her PM said that she was someone with a grasp on every political affair. In 1953, she was the head of state of 25 countries, but only 14 remain now. She was a member of the Commonwealth, ghost of the Empire, only kept alive through the queen's figure.
\par She met five popes. She was on many coins. She was one of the most admired women in the world. But now, all of this will change (her tornado blowjobs will never be the same). Everything in England is dressed in black now. No joyful music must be played. The coronation will be in a few months. There is a national mourning of ten days. Her coffin will be moved everywhere until Westminster, where the evil duke Philipula rests. The stock exchange will stop during the funeral (which really brings out the fun in funeral). The national anthem will change. No one became king a 73 like Charles the old man, former husband of lady D. Charles is cringe.
\par Some believe that George should become king because he is younger. Her son is indeed old and dull. Dispatch boxes are a very strange way to give confidential files to prominent government members. 20 countries among the 56 in the Commonwealth are monarchies.
\par THE QUEEN DIES BUT DOES NOT LIVE.

\subsection{USA}
FBI search on Trump's house. August, Mar-a-lago, Florida. Happened because american justice suspected crimes (obstruction to the law, removed government records, owning multiple classified documents). Once the president retire, they have to get their documents to the national archives, but he didn't give everything in january.
\par 15 boxes were found, some containing state secrets. Lots of personals items inside, too. Trump reacted and said he was shocked, but said he would have given it back if justice asked for it (in may, he had refused to give them back). He said all the documents found were already declassified. Trump is accusing Biden of abusing the presidential powers.
\par In the 4th of september, he held a meeting for the midterms where he used this as an argument for his cause. (William Bar is the chief of the department of justice.)


\section{Semaine du 19 au 23 septembre 2022}
\subsection{UK}
Actually, there's been nothing that wasn't about the queen in politics, so we're gonna talk about Shanila Bagum (?). She is a british 23 years old woman, and was radicalized, and went to Syria and joined the islamic state. She vanished from 2015 until 2019, where the UK gov decided she was a threat to the country, and removed her citizenship. Since then, she is in a camp in Syria, and trying to get back her citizenship. Her argument is that she was radicalized at 15, and was only a victim of the conflict.
\par What happened recently were revelations about the people smuggler who lead her into Syria. He was actually tied to canadian intelligence, and gave data to the embassy. This brought many questions about this loss of citizenship. Some believe it is a cover up for the fact the UK prioritized intelligence gathering over radicalized youths. Also, the "Nationality and borders act" strenghthened the UK government ability to strip people of citizenship and deny refugees a place in the UK. This targets muslim people the most, who don't feel like their rights are safe in the UK. White people would never get their citizenship taken from them.

\subsection{USA}
About the Mississipi water crisis : five days ago, the "boil water notice" was lifted. It required inhabitants of Mississipi to boil their water before use. What happened is that there was a big-ass flood in Mississipi, and the water system failed in Jackson (capital of Mississipi). There were only 7 water distributions in the entire city, and there were also rushes in the supermarkets to buy bottled water. 12 million bottles were distributed by the government (federal).
\par The ban was lifted when the system was repaired by the state government, the fiteenth of september. This news is important because it showcases the climate crisis and the floods it causes, and shows as well the poverty of Mississipi (tied to the segregation of the black population). After the abolition of slavery, Jackson became a city with less white boys than AA. It also showcases how poorly the infrastructure was taken care of. The segregation in Mississipi is a good exemple of environmental racism (segregation + climate crisis).
\par You can really easily use this as an example of the problems that the Build Back Better (BBB) bill is trying to solve.


\section{Semaine du 26 au 30 septembre 2022}
\subsection{UK (Nope, Federer land)}
Roger Federer played his last game against Nadal this week-end. He is a professionnal. He is also a tennisman. He is also from Switzerland. He founded the Roger Federer Foundation to help the poors. In his last game, he cried like a true soyman.

\subsection{USA}
New law in Arizona, banning abortion. In the last week, the USSC overruled Roe V Wade, set in 1973. The USSC voted that because there are now more conservative judges after Trump's presidency (6 cons et 3 libéraux).
\par Arizona is one of the first states to outright ban abortion. Mainly because of white christianity and republican leadership. People will have to go to other states for an abortion. The best solution against republican power is to vote blue in the midterms, like a wuss. Like a liberal cuck. Like a soyboy liberal cuckjack. I'm honestly running out of words to slander american liberals, I need to watch more Cucker Tarlson content.


\section{Semaine du 3 au 7 octobre 2022}
\subsection{USA}
Hurricane Ian, category 4. Went to south carolina end september. Killed more than an hundred people, emergency services are still looking for survivors. The storm outlined a lot of problems in the infrastructure. Studies show that climate change make hurricanes worse, so this showcases the dangers of climate change. Climate Change also increases rain.
\par In the US, contrary to France, most of the houses that were destroyed were not insured (because the law doesn't require it). The federal government has a program, but it is very limited (no one insured by a private company will be in it). The damages are so massive that many private insurances companies will go bankrupt according to economists. The solution is, of course, political action against climate change and reconstructing the infrastructure. 

\subsection{UK}
Yesterday, Liz Truss decided not to cut taxes to the richest people. Quite surprisingly, the people was against it. The pound hits its historic lowest. Liz Truss is bad with money, and Kamikwasi seems too. So they will probably cap benefits too.

\section{Semaine du 10 au 14 octobre 2022}
\subsection{USA}
Gun control in the USA : Judge blocked parts of NY gun law which would create new requirements for obtention of gun licence. For example, social media accounts need to be checked before giving a licence. The goal of the law was to reduce criminality in the city and the "ghost weapons" sold between persons. The NRA is against it and other groups like "Guns Owners of Amercica" are suing NY about it. Why isn't there progress for restrictive gun laws. There are pushes for laws after every mass shooting, but nothing happens. Mass shootings are at the core of many US issues. Death rate because of firearms is ten times higher than the OECD average.
\par Most gun owners are men (49 percents of men own one, 22 of women do), republican (44 percent for repubs and 20 for democrats) and in rural areas (41 in rural, 20 in cities). There are more guns in circulation than people in the USA. This gun culture seems to hail from the second amendment coming from the American Revolution, and its need for militias. It is recognized as a fundamental freedom. It's really easy to buy guns in the US, some states have them in supermarkets. There are also gun shows (often coming from the NRA) where no one runs background checks before selling guns.
\par The NRA is the biggest gun lobby, supporting Donald Trump (reciprocated). There is quite a lot of NRA speakers saying "To stop a bad guy with a gun, it takes a good guy with a gun." There are also schools where teachers are allowed to have gun training and get their guns in class (mostly in Utah). Any federal reform is impossible since the senate is divided on the subject, and lobbies are strong.
\par The USSC is arbitrating the suing between GOA and NYC. It expressed a ruling undermining secularity. Also, they already ruled in favor of RPA (gun association) against NYC. Eric Adams' mayor, who used to be a police officer, started a campaign based on regulations. Being written in the constitution makes the second amendment very hard to amend, contrary to the right to have an abortion. Reversal of usage of guns since second amendment : protect the state before, protect yourself from the state now.

\subsection{UK}
After the minibudget policy of Truss, the chancellor of the exchequer still needs money. There are a lot of debts for the government, more than what was forecast before. The Liz Truss government seems to think than tax cuts would improve growth, but basically every economy authority agree that it would have a minor effect. British economy is not going well and they don't know yet if they're gonna have a recession.

\section{Semaine du 14 au 19 novembre 2022}
\subsection{UK}
There was a COP27 recently, between the seventh and the eighteenth of nevember. They want to make a new treaty, to discuss a measurment of emissions. Next year will be the first assessment of progress since the first COP in 1992. Rishi SUnak decided to go to COP, going against what his party wanted to do first.
\par About Ukraine : Zelensky was present through video and said that we should do ecology, and that we should do peace too. In other news, some artists do things for climate. \par Oh and world leaders till came to Egypt by plane.

\subsection{USA}
Trump contested a tribunal summoning, after the alledged Biden win, there was a riot by his supporters in the capitol. He was told to go to court to talk about the situation. His attorneys maintain that the subpoena was illegal and that he has immunity. He also says he wasn't responsible, even though every testimony agrees on the fact he was responsible.
\par Out of the 900 accused for the Capitol Riot, 412 pleaded guilty. Trump promised that when he is elected again, he would pardon everyone.







\end{document}